### 2014-05-02 Article.tex
Add stuff

\section{Abstract}
In this contribution, we investigate the problem of "SwitchBoxes".
The goal is, given $n$ wires, to generate all the permutations of these wires by using "boxes",
 that swap two wires. We tried to minimize the number of boxes that were necessary.
We introduce a conjecture that puts our problem in relation with binary insertion sort. 
We successfully used a heavily optimized algorithm to prove this conjecture for small values of $n$.

\section{Introduction}
The SwitchBoxes problem is a combinatory problem. Given $n$ wires, (coming from the top), 
we try to generate all the permutations of these wires by using boxes. 
A box takes two wires, and is allowed to swap these wires. We can concatenate these boxes to get a configuration of boxes.
The configuration is said valid if, by swapping or not the wires on every box, we can obtain any permutation of the $n$ wires.

@@

>>>>

\section{Abstract}

In this contribution, we investigate the problem of "SwitchBoxes".  The goal is,
given $n$ wires, to generate all the permutations of these wires by using
"boxes", that swap two wires. We tried to minimize the number of boxes that were
necessary.  We introduce a conjecture that puts our problem in relation with
binary insertion sort.  We successfully used a heavily optimized algorithm to
prove this conjecture for small values of $n$.

\section{Introduction}

The SwitchBoxes problem is a combinatory problem. Given $n$ wires, (coming from
the top), we try to generate all the permutations of these wires by using boxes.
A box takes two wires, and is allowed to swap these wires. We can concatenate
these boxes to get a configuration of boxes.  The configuration is said valid
if, by swapping or not the wires on every box, we can obtain any permutation of
	the $n$ wires.

@@

% Part 0. Introduction
% Part 1. Conjecture
% Part 2. Optimisation
% Part 3. Pistes de recherche

\section{Our conjecture}

\subsection{First examples}

$n=2$ : $S_2(e_1) = (1,2)^{e_1}$

$n=3$ : $S_3(e_1,e_2,e_3) = (1,2)^{e_1} \circ (2,3)^{e_2} \circ (1,2)^{e_3}$

$n=4$ : fill in later

\subsection {Notation}

We abbreviate the previous notation in the following way :

$$S_2 = (1,2)$$

$$S_3 = (1,2)(2,3)(1,2)$$

$$S_4 = (1,2)(3,4)(1,3)(2,4)(1,2)$$

\section{Hypothesis box system}

We have found a box system that seems to generate all permutations for all $n$.
We have managed to prove that this box system is valid for small values of $n$
($n \leq 13$), and have found that the box systems were still valid when some
boxes were removed.

\subsection{The basis box configuration}

We first define the $q$-block at position $i$ by :

$$B(q,i) = (q,q+2^i)(q+1,q+1+2^i)\cdots(q+2^i-1)(q+2*2^i-1)$$

For example: 
$$B(0,i) = (i,i+1)$$
$$B(1,i) = (i, i+2)(i+1, i+3)$$
$$B(2, i) = (i,i+4)(i+1,i+5)(i+2,i+6)(i+3,i+7)$$

Then, for $n=2^p$ we define for $q < p$ the $(p,q)$-line by :

$$L(p,q) = B(q,0) B(q,2^{q+1}) \cdots B(q,2^p-2^{q+1})$$

For example:
$$L(3,0) = (0,1)(2,3)(4,5)(6,7)$$
$$L(3,1) = (0,2)(1,3)(4,6)(5,7)$$
$$L(3,2) = (0,4)(1,5)(2,6)(3,7)$$

We now conjecture that the following configuration generates all permutations
for $n=2^p$ :

$$S_{2^p}^0 = L(p,0) L(p,1) L(p,2) \cdots L(p,p-1) L(p,p-2) \cdots L(p,1) L(p,0)$$

For example :

$$
\begin{aligned}
	S_8^0 & = & L(3,0) L(3,1) L(3,2) L(3,1) L(3,0) \\
        & = & (0,1)(2,3)(4,5)(6,7) \\
		& & (0,2)(1,3)(4,6)(5,7) \\
		& & (0,4)(1,5)(2,6)(3,7) \\
		& & (0,2)(1,3)(4,6)(5,7) \\
        & & (0,1)(2,3)(4,5)(6,7)
\end{aligned}$$

\subsection{Truncation}

For $n$ which is not a power of two, we construct $S_n^0$ by taking
$S_{2^{log_2(n)}}^0$ and keeping only boxes $(i, j)$ having $i, j < n$.

For example, $S_5^0$ can be generated from $S_8^0$ and by removing quite a lot
of the boxes. We obtain the following solution :

$$S_5^0 = (0,1)(2,3)(0,2)(1,3)(0,4)(0,2)(1,3)(0,1)(2,3)$$

\subsection{Testing the box system}

\subsection{Useless box elimination}
